\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.2in,
  right = 0.2in,
  top = 0.2in,
  bottom = 0.0in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\head}[6]{
  \noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{#1}{\color{blue}{\LARGE {\underline{#2}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:#3}{\underline{#3}} $\mid$
      #4 $\mid$
       \href{#5}{\underline{Github}} $\mid$
       \href{#6}{\underline{LinkedIn}}
    }
  \end{tabular*}
  \vspace{-10pt}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    \small{#1}
  \end{addmargin}
}
\newcommand{\educationItem}[5]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \footnotesize{#1 in \textbf{#2}}  & \footnotesize{#3}\\
    \footnotesize{\textit{#4}} & \footnotesize{#5}\\\vspace{-5pt}
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    \footnotesize{\textbf{#1}: } & \footnotesize{#2}
  \end{tabular*}\vspace{-22pt}
}
\newcommand{\jobHeading}[3]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \small{{\href{#1}{#2}} \textbf{#3}} & \small{#4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}
\newcommand{\certItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    \footnotesize{\textbf{#1}: } & \footnotesize{#2}
  \end{tabular*}\vspace{-22pt}
}
\begin{document}

%   INTRO   %
\head
  {https://rhit.am/portfolio/} %1%
  {Rhitam Dutta} %2%
  {rhitamdutta1996@gmail.com} %3%
  {+91 7019679084} %4%
  {https://github.com/exthazor} %5%
  {https://www.linkedin.com/in/rhitam-dutta} %6%

%   EXPERIENCE   %
\section{Experience}
\sectionStart
 \jobHeading
    {Software Development Engineer}
    {March 2022 - now}
    {Wint Wealth | Backend Team}
  \listStart
    \bulletItem
    {Architected and executed the first-ever \textbf{Two Factor Authentication (2FA)} system for our Web and Mobile Apps, a move that effectively \textbf{eliminated security breaches}. This was a significant upgrade from the previous system where OTPs were managed by third-party vendors. I introduced an innovative approach of using Redis for temporary OTP storage. This led to a \textbf{90\% reduction in login issue tickets} and ensured our \textbf{platform’s compliance with SEBI security standards}. Today, my 2FA APIs are a cornerstone of our security infrastructure, serving \textbf{50,000+ active users per month}.}
\bulletItem
    {Developed the \textbf{SIM Binding protocol} for our platform, enhancing security by verifying SIM ownership. This was crucial for the Unity FD product, launched in December 2023. The protocol has enabled \textbf{200+ users} to securely purchase Unity FDs, generating \textbf{1.5+ lakh rupees in revenue}.}
    \bulletItem
    {Led the Strapi CMS integration into Wint's AWS infrastructure, transforming content management. Previously, updates to texts, colours, and SEO keywords were manually deployed by frontend engineers. I configured AWS's VPC, Route Tables, Internet Gateway, NAT Gateway, EC2, Elastic Beanstalk, CDN, S3, and RDS together to form a comprehensive Wint CMS powered by open source Strapi that enabled instant updates to textual information at both website and apps. Strapi APIs currently garner \textbf{100,000+ monthly reach} and showcased its value when a poorly visible modal in the bond referral version 3 was \textbf{redesigned and launched within an hour}, \textbf{boosting user interaction by 65\%}.}
 \bulletItem
    {Revamped Wint's bond referral program to version 3 in July 2023, enabling automatic distribution of earnings to referrers based on referees' bond interest repayment schedule. Leveraged AWS SNS, SQS, Lambda, Step Functions, and Razorpay X APIs to automate and streamline the repayment process, ensuring timely and accurate rewards. This strategic update attracted \textbf{40,000+ new customers} and generated \textbf{5+ crores of rupees in revenue to date}.}
 \bulletItem
    {Debugged and resolved a persistent issue in the Clevertap tracking platform, where user email IDs were being erroneously mixed. Approximately \textbf{4,000 users received emails about bond repayments they had not purchased}. By implementing a 2-minute delay in the tracking code through strategic use of SQS and Lambda functions, I effectively corrected the error.}
   \listEnd
  \jobHeading
    {Software Development Engineer}
    {August 2020 - February 2022}
    {Cerner Corporation | Cardiology Department}
  \listStart
    \bulletItem
    {Streamlined Cerner's Powerchart EMR workflows by developing a feature in Visual C++ and Oracle for correcting medical study mismatches without procedure restarts, enhancing clinical efficiency. }
 \bulletItem
    {Implemented the "inerror" datatype across both frontend (Visual C++) and backend (Java) components of Cerner's patient APIs. This involved adding a new field to accurately mark and handle patient data.}
 \bulletItem
    {Upgraded and deployed numerous proprietary Maven dependencies. }
   \bulletItem
   {Automated testing using Eggplant for various workflows.}
   \listEnd
\sectionEnd

%   PROJECTS   %
\section{Projects}
\sectionStart
\projectHeading
    {https://github.com/exthazor/CherryCityCottage-Frontend/}
    {Hotel Booking System}
    {(Strapi, Tailwind, AWS)}
    {January 2023}
  \listStart
    \bulletItem
      {Engineered a robust and user-friendly hotel booking system for Cherry City Cottage, a renowned hospitality establishment in Guwahati.}
  \listEnd
  \projectHeading
    {https://github.com/exthazor/rhitamdutta/}
    {Rhitam Dutta Online Coaching}
    {(Django, Vanilla JavaScript, AWS)}
    {August 2020}
  \listStart
    \bulletItem
      {In response to the pandemic, I launched an online coaching platform integrated into my website, providing a one-stop solution for fitness -- offering a variety of features to ensure a seamless and comprehensive fitness journey.}
  \listEnd
  \projectHeading
    {https://github.com/exthazor/angel}
    {Angel Bot}
    {(Discord.js, Discord-Akairo, TypeScript)}
    {May 2020}
  \listStart
    \bulletItem
    {Designed and built Angel, a versatile and engaging Discord bot. This open-source is enhancing user engagement and community management across several servers.}
  \listEnd
\sectionEnd

%   SKILLS   %
\section{Technical Skills}
\sectionStart
  \skillItem
    {Languages}
    {Kotlin, Python, Java, Javascript, C\#, PostgreSQL, Dart, Unix}
  \skillItem
    {Frameworks}
    {Spring Boot, Django, Express.js, Flutter, Next.js, Tailwind}
  \skillItem
    {Tools}
    {AWS, Git, Jira, Jenkins, Maven, Node.js, Docker, IntelliJ, Visual Studio Code, \LaTeX\ }
  \vspace{3pt}
\sectionEnd

%   CERTIFICATIONS & ACHIEVEMENTS   %
\section{Certifications \& Achievements}
\sectionStart
    \certItem 
     {AWS Certified Developer Associate} {Proficient in AWS-based application lifecycle management.}
    \certItem 
     {Powerlifting Silver Medalist} {Secured 2nd place in PRO League National Squat Championship, 2022.}
\sectionEnd


%   EDUCATION   %
\section{Education}
\sectionStart
  \educationItem
    {Bachelor of Technology} 
    {Information Technology} 
    {August 2016 - June 2020}
    {Manipal Institute of Technology} 
    {Minor in Big Data}
\sectionEnd

\end{document}